---
title: "Practical Machine Learning Assignment1"
output: html_document
---


First of all, load the libraries needed
```{r}
library(caret)
library(rpart)
library(randomForest)
```

## Prepossing data

```{r}
##### Load the data sets and replace the missing values with "NA"
train <- read.csv("pml-training.csv",na.strings = c("NA","","#DIV/0!"))
test <- read.csv("pml-testing.csv",na.strings = c("NA","","#DIV/0!"))
```

Because the training set is in large size, and both training and testing sets have more than 100 variables, I'd better delete some with a lot of NAs
```{r}
##### Delete the columns filled with NAs
train <- train[,colSums(is.na(train)) == 0]
test <- test[,colSums(is.na(test)) == 0]
```
Because the "X","username" and following columns contribute little to modeling, it is necessary to delete them, too.
```{r}
##### Delete the columns with useless variables
train<-train[,-c(1:7)]
test<-test[,-c(1:7)]
```
Although testing sets are given, it is still essential to separate testing data from training data, in order to determine the model
```{r}
##### Separte Training Data to allow Cross Validation
inTrain <- createDataPartition(y = train$classe, p = 0.75, list = FALSE)
subtraining <- train[inTrain, ]  
testtraining <- train[-inTrain, ]  
```
After data-washing, take a look at their dimensions
```{r}
##### Get the dimensions of datasets
dim(subtraining)   # 14718 obs. of 53 variables
dim(testtraining)  # 4904 obs. of 53 variables
```
## Model building
First, employ "rpart" method
```{r}
##### Create a CART model
modFit1<-train(classe~.,data=subtraining,method="rpart")
print(modFit1)
prediction1<-predict(modFit1,testtraining)
confusionMatrix(prediction1, testtraining$classe)
```
It is obvious from the result that the accuracy is low, therefore I try the randomforest model
```{r}
##### Create a randomforest model
modFit2<-train(classe~.,data=subtraining,method="rf",trControl=trainControl(number = 4))
print(modFit2)
prediction2<-predict(modFit2,testtraining)
confusionMatrix(prediction2, testtraining$classe)
```
It takes a long time to fit the randomforest model, but its accuracy is high. Weighing pros and cons, I decide to choose the randomforest method.
## Predict 20 different test cases
```{r}
##### Cross Validation
prediction3<-predict(modFit2,test)
prediction3
```
